### 2024-08-14 cluster-analysis.qmd
20240814 - WR types

```{r}
library("petersenlab")
library("mclust")
library("tidyverse")
library("plotly")
```

@@

```{r}
merged_data <- merged_data %>% 
  mutate(
    height_coalesced = coalesce(height, ht_numeric),
    weight_coalesced = coalesce(weight, wt),
    receptions_coalesced = pmax(receptions, rec.rec, na.rm = TRUE),
    receiving_air_yards_per_rec = receiving_air_yards / receptions
  )

@@

wrTypes_boostrap <- mclust::mclustBootstrapLRT(
  data = merged_dataWRs_cluster %>% select(-gsis_id, -display_name),
  modelName = "VVV") # ellipsoidal (variable volume, variable shape), variable orientation (for multivariate data)

@@

>>>>

```{r}
library("petersenlab")
library("mclust")
library("plotly")
library("tidyverse")
```

@@

```{r}
merged_data <- merged_data %>% 
  mutate(
    height_coalesced = coalesce(height, ht),
    weight_coalesced = coalesce(weight, wt),
    receptions_coalesced = pmax(receptions, rec.rec, na.rm = TRUE),
    receiving_air_yards_per_rec = receiving_air_yards / receptions
  )

@@

wrTypes_boostrap <- mclust::mclustBootstrapLRT(
  data = merged_dataWRs_cluster %>% select(-gsis_id, -display_name),
  modelName = "VVE") # ellipsoidal (variable volume, variable shape), equal orientation (for multivariate data)

@@

Type 1 WRs:

```{r}
merged_dataWRs_cluster %>% 
  filter(type == 1) %>% 
  select(display_name)
```

Type 2 WRs:

```{r}
merged_dataWRs_cluster %>% 
  filter(type == 2) %>% 
  select(display_name)
```

Type 3 WRs:

```{r}
merged_dataWRs_cluster %>% 
  filter(type == 3) %>% 
  select(display_name)
```
